The Splashback Radius of Planck-SZ clusters

### 2018-10-15 Paper_new/RSP_paper_new.tex
Added contamination estimate to paper

We exploit the XXX SDSS galaxy sample to calibrate our color cut (cite ???).
The SDSS galaxy sample is divided into a red and a blue galaxy population
using the color cut XXX (cite???). By cross matching the sample with our Pan-STARRS
catalog we can identify parts of the Pan-STARRS galaxies as red and blue galaxies,
respectively. Additionally, we assign the photometric redshifts from the SDSS sample to
the matched Pan-STARRS galaxies. The redshift dependent 
$g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut is then calibrated to exclude
red galaxies from being characterized as blue galaxies at a confidence level of 3$\sigma$.

@@

@@

@@

>>>>

We bin the galaxies into narrow redshift bins and produce a histogram of
the $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ colors of the galaxies in each bin. Due to
the Lyman-$\alpha$-break present in the red galaxy population, the two galaxy populations
separate in such a histogram and we fit a double Gaussian distribution to it.
Based on the fitted distribution we put a cut in color such that we can exclude a contamination
of the blue population by incorrectly characterized red galaxies with a confidence of 3$\sigma$.
Repeating this proceduce for each redshift bin we end up with a redshift dependent color cut that
separates the red from the blue population minimizing the contamination of the blue population by
red galaxies. Although being much simpler and faster than calculating the individual k-corrections
for each galaxy this procedure has its own shortcomings as discussed in Appendix~\ref{sec:Errors}.

@@

We note that, in principle it is possible that the blue galaxy population does not posses
a splashback feature but that due to our separation procedure outlined in Section~\ref{sec:Color}
some of the red galaxies are identified as blue ones and are contaminating the correlation function
of the blue population. Such a contamination could be caused by a scattering of some of the red galaxies
into the blue population due to the large photometric errors of the Pan-STARRS galaxies at faint magnitudes.
We tried to investigate the possiblity of that happening as outlined in 
Appendix~\ref{sec:Errors}. Unfortunately, we established that at the current state of the data we cannot
exclude such a contamination and the results derived using the color separated galaxy populations
should be used with caution therefore.

@@

The separation of the blue and red galaxy populations as described in 
Section~\ref{sec:Color} is prone to photometric errors. In order to 
assure our finding of a splashback feature in the blue galaxy population
a deeper galaxy catalog would be desirable. Again, the future survey
conducted with the Hyper Suprime-Cam could come to rescue.

@@

\section{Estimating the contamination of the blue galaxy population}
\label{sec:Errors}
In our separation procedure of the blue from the red galaxy population 
we assume the photometric magnitudes of the Pan-STARRS galaxies to be exact.
However, photometric errors could cause red galaxies to scatter into the blue
population which contaminates the correlation function and might be the cause 
for the splashback feature observed in the blue population. Therefore, we 
investigate the possiblity of such a contamination.

Firstly, we need to know how high such a contamination would have to be in order
to reproduce the splashback signal as seen in the observations given that the actual
blue poulation does not posses such a signal at all. We assume a simple $r^{-1.5}$ power 
law for the correlation signal of the blue population which by construction cannot cause a splashback feature. Then,
we simulate a contamination of the population by adding some of the accordingly rescaled 
correlation signal of the red population, which does posses a splashback feature.
We find that a contamination of at least 20\% is necessary to reproduce the observed
splashback signal.

Next we estimate the photometric errors of the Pan-STARRS galaxies in each one of the used
bands (namely $i_{PS}, g_{PS}, r_{PS}$). Since we chose galaxies with $15.0 \leq i_{PS} \leq 21.5$
for our analysis we consider the $i_{PS}$ errors as given in the Pan-STARRS survey of only 
the galaxies in this magnitude range. We fit a Gaussian to their distribution and use a conservative $3\sigma$ confidence
estimate for the photometric error in the $i_{PS}$ band. We repeat the same analysis for the
$g_{PS}$ and $r_{PS}$ bands, but using magnitude ranges which are shifted by the mean magnitude
differences between the $i_{PS}$ band and the $g_{PS}$ and $r_{PS}$ bands, respectively.
The histograms of the errors as well as the estimated photometric errors are shown in
Figure~\ref{fig:photoerrors}. We find similar photometric errors in the $i_{PS}$ (63 mmag)
and $r_{PS}$ band (64 mmag) but a larger error in the $g_{PS}$ band of 81 mmag.

\begin{figure}
\centering{
    \includegraphics[scale=0.6]{errors.pdf}}
\caption{Histograms of the photometric errors in the used $i_{PS}, g_{PS}, r_{PS}$ bands.
The errors were taken dirrectly from the Pan-STARRS survey and sampled for galaxy type 
objects in the magniude range $15.0 \leq i_{PS} \leq 21.5$, $16.3 \leq g_{PS} \leq 22.8$ and $15.4 \leq r_{PS} \leq 21.9$, respectively. 
The upper photometric error limits at $3\sigma$
confidence are listed in the upper right of the figure.}
    \label{fig:photoerrors}•
\end{figure}

Finally, we estimate the contamination of the blue galaxy population given the cut in $g_{PS} - r_{PS}$
color that we used to separate the two populations. We start the same way as we established the cut:
By taking narrow redshift bins and then by binning the $g_{PS} - r_{PS}$ colors of the galaxies in each
redshift bin. Then we proceed by fitting a double Gaussian to the color distribution in each redshift bin
(indicated by the solid, accordingly colored lines in Figure~\ref{fig:histogram}). We put the cut which
separates the two distributions from each other at a $g_{PS} - r_{PS}$ color such that red galaxies are
excluded from being incorrectly characterized as blue galaxies at a confidence level of $3\sigma$ (indicated
by the solid, vertical, black line). At that point the fractional contribution of the red population reads 
$\sim 40\%$ which corresponds to a free field galaxy sample. In order to model the distribution inside of 
the cluster region we rescale the red distribution such that we end up with a fractional contribution of 
the red population of $65\%$. We do now take into account the estimated photometric errors in the $g_{PS}$ and
$r_{PS}$ bands by broadening the Gaussian distributions accordingly. The contamination is then estimated as:
\begin{equation}
\sum_{z=0.03}^{0.33} \int_{-\infty}^{cut(z)} 1 + \frac{\mathcal{N}_r(g-r)}{\mathcal{N}_b(g-r)} \mathrm{d}(g-r)
\end{equation}
where the sum runs over all redshift bins, the integration is performed over the $g_{PS} - r_{PS}$ color up 
to the redshift dependent cut $cut(z)$ separating the two distributions and $\mathcal{N}_r(g-r)$ and $\mathcal{N}_b(g-r)$
representing the broadened Gaussian distributions of the red and blue population, respectively
(dashed, accordingly colored curves). With the described analysis we calculate a contamination of 24\%, which would
be high enough to explain the observed splashback signal of the blue galaxy population solely by red galaxies
that scattered into the blue population. However, this cannot be taken as disproof of the existence of a splashback
feature in the blue galaxy population. The contamination estimate strongly depenends on two factors: Firstly, on the 
confidence at which one wants to exclude red galaxies from being misidentified as blue galaxies and secondly on the
method one uses to estimate the photometric errors (magnitude range and the conservatism of the error estimate).
Depending on the approach we got contamination estimates ranging from 0.0001\% to 60\%. Therefore, at the current
state it cannot be concisely established if the observed splashback feature stems from a contamination of red
galaxies or not. A deeper galaxy catalog with smaller photometric errors, especially in the $g_{PS}$ band is
required to shed light on this matter.

\begin{figure}
\centering{
    \includegraphics[scale=0.6]{best_hist_58.pdf}}
\caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
    \label{fig:histogram}•
\end{figure}
